---
name: Luke
surname: Ozsanlav-Harris
position: "Ecologist"
address: "Witney, Oxfordshire "
www: lukeozsanlav.github.io/LukeOzHarris/
email: lukeozharris@outlook.com
github: LukeOzsanlav
orcid: 0000-0003-3889-6722
headcolor: 009ACD
date: "`r format(Sys.time(), '%B %Y')`"
fontsize: 10pt
output:
  vitae::awesomecv:
    page_total: true
header-includes:
  - \usepackage{leading}
  - \leading{16pt}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```


# Summary

**Data**: Statistical Modelling | Spatial Data Analysis | Biologging Data | R | Javascript | QGIS 

**Writing**: Scientific | Technical Reports | Public Communication 

**Interpersonal**: Stakeholder Interactions | Collaboration | Project Management

**Interests**: Avian Migration | Conservation | Animal Movement 



\faIcon{university} Education
==================================

```{r education}
tribble(
  ~ study, ~ university, ~ loc, ~ dates, ~ details,
    "PhD in Ecology", "University of Exeter","Penryn, Cornwall", "2019 - 2022", "Dissertation: Understanding the decline of a long-distance migratory bird, The Greenland White-fronted Goose.",
    "MSc in Applied Ecology (Distinction)", "University of Exeter","Penryn, Cornwall", "2017 - 2018", "Dissertation: Understating the genetic basis of colour polymorphism in the green peach aphid.",
  "BSc Natural Sciences (2:1)", "University of Durham", "Durham", "2014 - 2017", "Literature Review: The decline of farmland birds in the UK.",
) %>%  
  detailed_entries(university, dates, study, loc, details, .protect=FALSE)
```




\faIcon{briefcase} Employment
============================================

```{r}
tribble(
  ~ study, ~ university, ~ dates, ~ details,
    "RSPB", "Conservation Scientist", "Sep 2023 - today", "Ran stakeholder workshops to co-develop future landscape conservation strategies",
    "RSPB", "Conservation Scientist", "Sep 2023 - today", "Carried out predicitve scenario modelling to develop and test which future conservation strategies would provide the biggest benefits to lowland breeding waders in the UK",
  "MarPAMM funded project: Isle of Rum Manx Shearwater census", "Spatial analyst & Fieldwork", "May - June 2021", "Surveyed the Manx shearwater colony, carrying out habitat and burrow occupancy surveys.",
  "MarPAMM funded project: Isle of Rum Manx Shearwater census", "Spatial analyst & Fieldwork", "May - June 2021", "Led spatial analysis for the final population estimate; manipulated Sentinel imagery and digital elevation models to build a predictive spatially explicit model that calculated occupied burrow density over the entire colony.",
  "JNCC Consultant: Review of avoidance rates for collision risk modelling of seabirds", "Analyst and report lead author", "Jan - Feb 2022", "Link to report produced within short 6 weeks deadline: https://hub.jncc.gov.uk/assets/de5903fe-81c5-4a37-a5bc-387cf704924d ",
  "JNCC Consultant: Review of avoidance rates for collision risk modelling of seabirds", "Analyst and report lead author", "Jan - Feb 2022", "Recalculation of avoidance rates in R and sensivity analysis to test the effect of various input parameters.",
  "JNCC Consultant: Review of avoidance rates for collision risk modelling of seabirds", "Analyst and report lead author", "Jan - Feb 2022", "Updated avoidance rates were detailed in a technical report and results were presented to marine scientist and windfarm industry stakeholders.",
  "Wildfowl and Wetlands Trust", "Research Officer", "Oct 2022 - April 2023", "Publish work carried out during my PhD in international scientific journals.",
  "Wildfowl and Wetlands Trust", "Research Officer", "Oct 2022 - April 2023", "Manage and curate large waterfowl tracking data sets, including upload to online repositories.",
  "Wildfowl and Wetlands Trust", "Research Officer", "Oct 2022 - April 2023", "Write guide to help researchers with the processing and visualisation of animal tracking data in R."
  
) %>%  
  detailed_entries(with =study, when =dates, what = university, why =details)
```



\faIcon*{file} Publications
===========================

For a list of publications see my [**google scholar profile.**](https://scholar.google.co.uk/citations?user=9VyBol4AAAAJ&hl=en)


1. Langley, L. P., Lang, S. D. J., **Ozsanlav-Harris, L.**, & Trevail, A. M. (2024). ExMove: An open-source toolkit for processing and exploring animal-tracking data in R. *Journal of Animal Ecology*, *93* (7), 784-795. https://doi.org/10.1111/1365-2656.14111 

2. **Ozsanlav-Harris, L.**, Burgess, M. D., Hilton, G. M., & Bearhop, S. (2023). Changes in the spatial patterns of avian migrations: Evidence, mechanisms and causes. *Diversity and Distributions*, *29* (12), 1527–1545. https://doi.org/10.1111/ddi.13785

3. **Ozsanlav-Harris, L.**, Hilton, G. M., Griffin, L. R., Walsh, A. J., Cao, L., Weegman, M. D., & Bearhop, S. (2023). Differing drivers of decline within a migratory metapopulation has implications for future conservation. *Ecology and Evolution*, *13* (7). https://doi.org/10.1002/ece3.10281


4. McIntosh, A. L. S., **Ozsanlav-Harris, L.**, Taggart, M. A., Shaw, J. M., Hilton, G. M., & Bearhop, S. (2023). Incidence of lead ingestion in managed goose populations and the efficacy of imposed restrictions on the use of lead shot. *Ibis*, *165* (4), 1397–1413. https://doi.org/10.1111/ibi.13210


5. Trissi, N., Troczka, B. J., **Ozsanlav-Harris, L.**, Singh, K. S., Mallott, M., Aishwarya, V., O’Reilly, A., Bass, C., & Wilding, C. S. (2023). Differential regulation of the Tor gene homolog drives the red/green pigmentation phenotype in the aphid Myzus persicae. *Insect Biochemistry and Molecular Biology*, *153*, 103896. https://doi.org/10.1016/j.ibmb.2022.103896

6. **Ozsanlav-Harris, L.**, Griffin, L., Weegman, M. D., Cao, L., Hilton, G. M., & Bearhop, S. (2022). Wearable reproductive trackers: quantifying a key life history event remotely. *Animal Biotelemetry*, *10* (24), 1–15. https://doi.org/10.1186/s40317-022-00298-8 

In press

7. **Ozsanlav-Harris, L.**, McIntosh, A. L. S., Griffin, Hilton, G. M., L., Cao, L., Shaw, J. M. & Bearhop, S. (In press) Contrasting effects of shooting disturbance on the movement and behaviour of sympatric wildfowl species. *Ecological Applications*





\faIcon{cogs} Research Skills
===========================

```{r}
tribble(
  ~ heading, ~ details,
  "Data Analysis", "Statistical analysis in R including; generalized mixed effects models incorporating spatial/temporal autocorrelation, time to event/survival modelling and bayesian generlaized linear modelling with brms",
  "Data Analysis", "Spatial data manipulation and analysis in Google earth engine, QGIS and R (using sf & terra packages)",
  "Data Analysis", "Download, manipulation and analysis of remote sensing data, e.g. MODIS, Sentinel, ECMFW and NCEP",
  "Data Analysis", "Collating, analysing and interpreting large databases (more than 250 million biologging data points)",
  "Data Analysis", "Machine learning analysis, e.g. Random Forests, clustering analysis and support vector machines",
  "Collaboration", "Carrying out research with multiple partners, e.g. WWT, JNCC, BTO, RSPB, SNH, to acheive mutualistic goals",
  "Collaboration", "Engagement with local stakeholders, e.g. with farmers on Islay, Scotland while researching contentious goose management cull",
  "Fieldwork", "Organised logistics for teams to catch birds and deploy biologging devices at various UK sites, interacting with various local stakeholders and organisations (e.g. NatureScot, WWT, local councils and farmers) "
) %>%  
  detailed_entries(what = heading, why = details)
```



\faIcon{comments} Presentations/Communication
===========================

```{r}
tribble(
  ~ study, ~ university, ~ dates, ~ details,
  "Scottish Goose Forum", "Invited Seminar", "2024", "Title: The decline of the Islay population of Greenland White-fronted Geese",
  "University of Lund", "Invited Seminar", "2022", "Title: Differing drivers of decline within a metapopulation has implications for future conservation",
    "BOU Avian Reproduction Conference", "Poster", "2022", "Title: Differing demographic drivers of low reproductive success within a high artic migrant meta-population",
  "Goose News", "Magazine Atricle", "2021", "Article on the research carried out during my PhD research to a broader non-academic audience",
  "Glengoyne Distillery Website", "Blog Posts", "2021", "Multiple blog posts for a funding partner website, conveying the findings of my research to their customers.",
  
) %>%  
  detailed_entries(with =study, when =dates, what = university, why =details, .protect=FALSE)
```






\faIcon{pen-fancy} References
===========================

```{r}
tribble(
  ~ Name, ~ Email, ~ University, ~ post,
  "Prof Staurt Bearhop", "S.Bearhop@exeter.ac.uk", "University of Exeter", "Professor in Animal Ecology",
  "Dr Robert Hawkes", "robert.hawkes@rspb.org.uk", "RSPB", "Conservation Scientist",
  
) %>%  
  detailed_entries(with = Name, when = post, what = Email, where = University, .protect=FALSE)
```