%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{009ACD}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Luke}{Ozsanlav-Harris}

\position{Spatial Ecologist}
\address{5 Quaintways, Cheshire, UK}

\email{\href{mailto:lo288@exeter.ac.uk}{\nolinkurl{lo288@exeter.ac.uk}}}
\homepage{lukeozsanlav.github.io/LukeOzHarris/}
\orcid{0000-0003-3889-6722}
\github{LukeOzsanlav}
\twitter{Luke\_ozharris}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{leading}
\leading{18pt}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {July 2023}
    {Luke Ozsanlav-Harris~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{skills-summary}{%
\section{Skills Summary}\label{skills-summary}}

\textbf{Data}: Statistical Modelling \textbar{} Spatial Data Analysis
\textbar{} Biologging Data \textbar{} R \textbar{} Shiny \textbar{} QGIS
\textbar{} Git

\textbf{Writing}: Scientific \textbar{} Technical Reports \textbar{}
Public Communication

\textbf{Interpersonal}: Stakeholder Engagement \textbar{} Collaboration
\textbar{} Project Management

\hypertarget{education}{%
\section{\texorpdfstring{\faIcon{university}
Education}{ Education}}\label{education}}

\begin{cventries}
    \cventry{University of Exeter}{PhD in Ecology}{Penryn, Cornwall}{2019 - 2022}{\begin{cvitems}
\item Dissertation: Understanding the decline of a long-distance migratory bird, The Greenland White-fronted Goose.
\end{cvitems}}
    \cventry{University of Exeter}{MSc in Applied Ecology (Distinction)}{Penryn, Cornwall}{2017 - 2018}{\begin{cvitems}
\item Dissertation: Understating the genetic basis of colour polymorphism in the green peach aphid.
\end{cvitems}}
    \cventry{University of Durham}{BSc Natural Sciences (2:1)}{Durham}{2014 - 2017}{\begin{cvitems}
\item Literature Review: The decline of farmland birds in UK.
\end{cvitems}}
\end{cventries}

\hypertarget{employment}{%
\section{\texorpdfstring{\faIcon{briefcase}
Employment}{ Employment}}\label{employment}}

\begin{cventries}
    \cventry{Spatial analyst \& Fieldwork}{MarPAMM funded project: Isle of Rum Manx Shearwater census}{}{May - June 2021}{\begin{cvitems}
\item Surveyed the Manx shearwater colony, carrying out habitat and burrow occupancy surveys.
\item Led spatial analysis for the final population estimate; manipulated Sentinel imagery and digital elevation models to build a predictive spatially explicit model that calculated burrow nesting bird density over the entire colony.
\end{cvitems}}
    \cventry{Analyst and report lead author}{JNCC Consultancy: Review of avoidance rates for collision risk modelling of seabirds}{}{Jan - Feb 2022}{\begin{cvitems}
\item Link to the report produced within short deadline (6 weeks): https://hub.jncc.gov.uk/assets/de5903fe-81c5-4a37-a5bc-387cf704924d
\item Recalculation of avoidance rates in R and sensivity analysis to test the effect of various input parameters.
\item Updated avoidance rates were detailed in a technical report and results were presented to marine scientist and windfarm industry stakeholders.
\end{cvitems}}
    \cventry{Research Officer}{Wildfowl and Wetlands Trust}{}{Oct 2022 - April 2023}{\begin{cvitems}
\item Publish work carried out during my PhD in international scientific journals.
\item Manage and curate waterfowl large tracking data sets, including upload to online repositories.
\item Write guide to help researchers with the processing and visualisation of animal tracking data in R.
\end{cvitems}}
\end{cventries}

\hypertarget{publications}{%
\section{\texorpdfstring{\faIcon*{file}
Publications}{ Publications}}\label{publications}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-ozsanlav-harris2023}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Ozsanlav-Harris, L., Hilton, G. M., Griffin, L. R.,
Walsh, A. J., Cao, L., Weegman, M. D., \& Bearhop, S. (2023). Differing
drivers of decline within a migratory metapopulation has implications
for future conservation. \emph{Ecology and Evolution}, \emph{13}(7).
\url{https://doi.org/10.1002/ece3.10281}}

\leavevmode\vadjust pre{\hypertarget{ref-mcintosh2023}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{McIntosh, A. L. S., Ozsanlav-Harris, L., Taggart, M. A.,
Shaw, J. M., Hilton, G. M., \& Bearhop, S. (2023). Incidence of lead
ingestion in managed goose populations and the efficacy of imposed
restrictions on the use of lead shot. \emph{Ibis}.
\url{https://doi.org/10.1111/ibi.13210}}

\leavevmode\vadjust pre{\hypertarget{ref-trissi2023}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Trissi, N., Troczka, B. J., Ozsanlav-Harris, L., Singh,
K. S., Mallott, M., Aishwarya, V., O'Reilly, A., Bass, C., \& Wilding,
C. S. (2023). Differential regulation of the Tor gene homolog drives the
red/green pigmentation phenotype in the aphid Myzus persicae.
\emph{Insect Biochemistry and Molecular Biology}, \emph{153}, 103896.
\url{https://doi.org/10.1016/j.ibmb.2022.103896}}

\leavevmode\vadjust pre{\hypertarget{ref-ozsanlav-harris2022}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Ozsanlav-Harris, L., Griffin, L. R., Weegman, M. D.,
Cao, L., Hilton, G. M., \& Bearhop, S. (2022). Wearable reproductive
trackers: quantifying a key life history event remotely. \emph{Animal
Biotelemetry}, \emph{10}(1).
\url{https://doi.org/10.1186/s40317-022-00298-8}}

In Review

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-ozsanlav-harris2022}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Ozsanlav-Harris, L., Burgess, M., \& Bearhop, S. (2023).
Changes in the spatial patterns of avian migrations: Causes, mechanisms
and consequences. In \emph{Diveristy and Distributions}.}

\leavevmode\vadjust pre{\hypertarget{ref-ozsanlav-harris2023a}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Ozsanlav-Harris, L., Phillips, R., Bailey, J., Langley,
L., Wilson, K., Inger, R., \& Bearhop, S. (2023). \emph{Exploring the
origins of vagrant yellow-browed warblers in western europe}.
\url{http://dx.doi.org/10.22541/au.167832183.32508222/v1}}

\leavevmode\vadjust pre{\hypertarget{ref-ozsanlav-harris2023c}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Ozsanlav-Harris, L., McIntosh, A. L. S., Griffin, L. R.,
Hilton, G. M., Cao, L., Shaw, J. M., \& Bearhop, S. (2023). Contrasting
effects of shooting disturbance on the movement and behaviour of
sympatric wildfowl species. In \emph{Ecological Applications}.}

\leavevmode\vadjust pre{\hypertarget{ref-langley2023}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Langley, L. P., Lang, S., Ozsanlav-Harris, L., \&
Trevail, A. (2023). ExMove: An open-source toolkit for processing and
exploring animal tracking data in r. In \emph{Journal of Animal
Ecology}. \url{http://dx.doi.org/10.1101/2023.05.16.540922}}

\hypertarget{research-skills}{%
\section{\texorpdfstring{\faIcon{cogs} Research
Skills}{ Research Skills}}\label{research-skills}}

\begin{cventries}
    \cventry{Data Analysis}{}{}{}{\begin{cvitems}
\item Statistical analysis including; generalized mixed effects models incorporating spatial/temporal autocorrelation, time to event/survival modelling and bayesian generlaized linear modelling with brms
\item Spatial data manipulation and analysis in QGIS and R (using sf & terra package).
\item Download, manipulation and analysis of remote sensing data, e.g. MODIS, Sentinel, ECMFW and NCEP.
\item Curating large databases (more than 250 million data points), including integration with online databases.
\item Analysing animal movement data, e.g. Hidden Markov models, change point analysis, continuous time movement modelling and habitat selection analysis.
\item Machine learning analysis, e.g. classifying accelerometer data using random forests.
\end{cvitems}}
    \cventry{Collaboration}{}{}{}{\begin{cvitems}
\item Carrying out research with multiple partners, e.g. WWT, JNCC, BTO, RSPB, SNH, to acheive mutualistic goals
\item Engagement with local stakeholders, particularly rural farmers on Islay, Scotland while researching contentious goose management cull
\end{cvitems}}
    \cventry{Fieldwork}{}{}{}{\begin{cvitems}
\item Organised logistics for teams to catch birds and deploy biologging devices at various UK sites, interacting with various local stakeholders and organisations (e.g. NatureScot, WWT and local councils) 
\end{cvitems}}
\end{cventries}

\hypertarget{presentationscommunication}{%
\section{\texorpdfstring{\faIcon{comments}
Presentations/Communication}{ Presentations/Communication}}\label{presentationscommunication}}

\begin{cventries}
    \cventry{Invited Seminar (academic)}{University of Lund}{}{2022}{\begin{cvitems}
\item Title: Differing drivers of decline within a metapopulation has implications for future conservation
\end{cvitems}}
    \cventry{Poster (academic)}{BOU Avian Reproduction Conference}{}{2022}{\begin{cvitems}
\item Title: Differing demographic drivers of low reproductive success within a high artic migrant meta-population
\end{cvitems}}
    \cventry{Talk (academic)}{Centre for Ecology and Conservation Symposium}{}{2021}{\begin{cvitems}
\item Title: Remotely understanding population decline in a high-arctic nesting goose
\end{cvitems}}
    \cventry{Invited Atricle (magazine)}{Goose News}{}{2021}{\begin{cvitems}
\item Magazine-style article on the research carried out during my PhD research to a broader non-academic audience
\end{cvitems}}
    \cventry{Blog Posts}{Glengoyne Distillery Website}{}{2021}{\begin{cvitems}
\item Multiple blog posts for a funding partner website, conveying the findings of my research to their customers.
\end{cvitems}}
\end{cventries}

\hypertarget{references}{%
\section{\texorpdfstring{\faIcon{pen-fancy}
References}{ References}}\label{references}}

\begin{cventries}
    \cventry{S.Bearhop@exeter.ac.uk}{Prof Staurt Bearhop}{University of Exeter}{Professor in Animal Ecology}{}\vspace{-4.0mm}
    \cventry{R.Sherley@exeter.ac.uk}{Dr Richard Sherley}{University of Exeter}{Senior Lecturer in Marine Vertebrate Ecology}{}\vspace{-4.0mm}
\end{cventries}


\label{LastPage}~
\end{document}
