---
name: Luke
surname: Ozsanlav-Harris
position: "Spatial Ecologist"
address: "5 Quaintways, Cheshire, UK"
www: lukeozsanlav.github.io/LukeOzHarris/
email: "lo288@exeter.ac.uk"
twitter: Luke_ozharris
github: LukeOzsanlav
orcid: 0000-0003-3889-6722
headcolor: 009ACD
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
header-includes:
  - \usepackage{leading}
  - \leading{18pt}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```


# Skills Summary

**Data**: Statistical Modelling | Spatial Data Analysis | Biologging Data | R | Shiny | QGIS | Git

**Writing**: Scientific | Technical Reports | Public Communication 

**Interpersonal**: Stakeholder Engagement | Collaboration | Project Management



\faIcon{university} Education
==================================

```{r education}
tribble(
  ~ study, ~ university, ~ loc, ~ dates, ~ details,
    "PhD in Ecology", "University of Exeter","Penryn, Cornwall", "2019 - 2022", "Dissertation: Understanding the decline of a long-distance migratory bird, The Greenland White-fronted Goose.",
    "MSc in Applied Ecology (Distinction)", "University of Exeter","Penryn, Cornwall", "2017 - 2018", "Dissertation: Understating the genetic basis of colour polymorphism in the green peach aphid.",
  "BSc Natural Sciences (2:1)", "University of Durham", "Durham", "2014 - 2017", "Literature Review: The decline of farmland birds in UK.",
) %>%  
  detailed_entries(university, dates, study, loc, details, .protect=FALSE)
```



\faIcon{briefcase} Employment
============================================

```{r}
tribble(
  ~ study, ~ university, ~ dates, ~ details,
  "MarPAMM funded project: Isle of Rum Manx Shearwater census", "Spatial analyst & Fieldwork", "May - June 2021", "Surveyed the Manx shearwater colony, carrying out habitat and burrow occupancy surveys.",
  "MarPAMM funded project: Isle of Rum Manx Shearwater census", "Spatial analyst & Fieldwork", "May - June 2021", "Led spatial analysis for the final population estimate; manipulated Sentinel imagery and digital elevation models to build a predictive spatially explicit model that calculated burrow nesting bird density over the entire colony.",
  "JNCC Consultancy: Review of avoidance rates for collision risk modelling of seabirds", "Analyst and report lead author", "Jan - Feb 2022", "Link to the report produced within short deadline (6 weeks): https://hub.jncc.gov.uk/assets/de5903fe-81c5-4a37-a5bc-387cf704924d",
  "JNCC Consultancy: Review of avoidance rates for collision risk modelling of seabirds", "Analyst and report lead author", "Jan - Feb 2022", "Recalculation of avoidance rates in R and sensivity analysis to test the effect of various input parameters.",
  "JNCC Consultancy: Review of avoidance rates for collision risk modelling of seabirds", "Analyst and report lead author", "Jan - Feb 2022", "Updated avoidance rates were detailed in a technical report and results were presented to marine scientist and windfarm industry stakeholders.",
  "Wildfowl and Wetlands Trust", "Research Officer", "Oct 2022 - April 2023", "Publish work carried out during my PhD in international scientific journals.",
  "Wildfowl and Wetlands Trust", "Research Officer", "Oct 2022 - April 2023", "Manage and curate waterfowl large tracking data sets, including upload to online repositories.",
  "Wildfowl and Wetlands Trust", "Research Officer", "Oct 2022 - April 2023", "Write guide to help researchers with the processing and visualisation of animal tracking data in R.",
  
) %>%  
  detailed_entries(with =study, when =dates, what = university, why =details)
```



\faIcon*{file} Publications
===========================

```{r}
bibliography_entries("PublishedPapers.bib") %>%
  arrange(desc(issued), issued)

```



In Review   

```{r}
bibliography_entries("Preprint_references.bib") %>%
  arrange(desc(author$family), issued)

```



\faIcon{cogs} Research Skills
===========================

```{r}
tribble(
  ~ heading, ~ details,
  "Data Analysis", "Statistical analysis including; generalized mixed effects models incorporating spatial/temporal autocorrelation, time to event/survival modelling and bayesian generlaized linear modelling with brms",
  "Data Analysis", "Spatial data manipulation and analysis in QGIS and R (using sf & terra package).",
  "Data Analysis", "Download, manipulation and analysis of remote sensing data, e.g. MODIS, Sentinel, ECMFW and NCEP.",
  "Data Analysis", "Curating large databases (more than 250 million data points), including integration with online databases.",
  "Data Analysis", "Analysing animal movement data, e.g. Hidden Markov models, change point analysis, continuous time movement modelling and habitat selection analysis.",
  "Data Analysis", "Machine learning analysis, e.g. classifying accelerometer data using random forests.",
  "Collaboration", "Carrying out research with multiple partners, e.g. WWT, JNCC, BTO, RSPB, SNH, to acheive mutualistic goals",
  "Collaboration", "Engagement with local stakeholders, particularly rural farmers on Islay, Scotland while researching contentious goose management cull",
  "Fieldwork", "Organised logistics for teams to catch birds and deploy biologging devices at various UK sites, interacting with various local stakeholders and organisations (e.g. NatureScot, WWT and local councils) "
) %>%  
  detailed_entries(what = heading, why = details, .protect=FALSE)
```



\faIcon{comments} Presentations/Communication
===========================

```{r}
tribble(
  ~ study, ~ university, ~ dates, ~ details,
  "University of Lund", "Invited Seminar (academic)", "2022", "Title: Differing drivers of decline within a metapopulation has implications for future conservation",
    "BOU Avian Reproduction Conference", "Poster (academic)", "2022", "Title: Differing demographic drivers of low reproductive success within a high artic migrant meta-population",
  "Centre for Ecology and Conservation Symposium", "Talk (academic)", "2021", "Title: Remotely understanding population decline in a high-arctic nesting goose", 
  "Goose News", "Invited Atricle (magazine)", "2021", "Magazine-style article on the research carried out during my PhD research to a broader non-academic audience",
  "Glengoyne Distillery Website", "Blog Posts", "2021", "Multiple blog posts for a funding partner website, conveying the findings of my research to their customers.",
  
) %>%  
  detailed_entries(with =study, when =dates, what = university, why =details, .protect=FALSE)
```



\faIcon{pen-fancy} References
===========================

```{r}
tribble(
  ~ Name, ~ Email, ~ University, ~ post,
  "Prof Staurt Bearhop", "S.Bearhop@exeter.ac.uk", "University of Exeter", "Professor in Animal Ecology",
  "Dr Richard Sherley", "R.Sherley@exeter.ac.uk", "University of Exeter", "Senior Lecturer in Marine Vertebrate Ecology",
  
) %>%  
  detailed_entries(with = Name, when = post, what = Email, where = University, .protect=FALSE)
```



